\documentclass[10pt,conference]{IEEEtran}

\usepackage{url,graphicx,subfigure,algcompatible,comment,amsmath,units,epsfig,threeparttable,multirow,colortbl,booktabs,setspace,textcomp}


\usepackage[ruled]{algorithm2e}

\title{An Agile Migration Framework for Analog Layout Design}
\author{
\IEEEauthorblockN{Po-Cheng Pan\IEEEauthorrefmark{1}, Prof. Hung-Ming Chen\IEEEauthorrefmark{1}\\}
\IEEEauthorblockA{\IEEEauthorrefmark{1}Institute of Electronics and SoC Center, National Chiao Tung University, Hsinchu, Taiwan\\}
\IEEEauthorblockA{Email: benbean.ee96g@g2.nctu.edu.tw; hmchen@mail.nctu.edu.tw}

  %\thanks{
  %{\scriptsize
  %  This work was partially supported by the National Science Council of Taiwan ROC under grant No. NSC 102-2220-E-009-024
    

  %  \noindent
  %  978-1-4799-1071-7/13/\$31.00 \copyright2013 IEEE }
  %}
}

\begin{document}

\maketitle

\begin{abstract}
  Layout generation in the late analog CMOS design is challenging by its increasing layout constraints and performance requirements. However, iterative refinement on manual design damages the productivity of analog layout. Therefore, it is more efficient to enroll the know-how from existing design instead of generating a new one. To contend with time-consuming analog layout for more possibilities, this software aims to demonstrate a fast layout prototyping framework for migration purpose into real layout design.

  In our framework, a reference analog layout design is given to generate potential layout candidates at the objective technology. The demonstration includes the original layout, the extracted topology with placement and routing, the generated layout figures, the dumped layout results and the simulated results. This procedure of migration provides a convincing exhibition of our migration framework.
\end{abstract}

\input{content.tex}


\bibliographystyle{IEEEtran}
\bibliography{IEEEfull,IEEEabrv,IEEEexample,reference}

\end{document}